%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\pdfminorversion=4

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{amsmath}    			% ams packages for mathematics environment    
\usepackage{amssymb}
\usepackage{amsfonts}
%\usepackage{amsthm}

\usepackage{graphicx}  				% Versatile graphics manipulation options

\usepackage[croatian]{babel}  % Croatian typographical rules and hyphenation patterns 
\usepackage[utf8]{inputenc}  	% Encoding of Croatian characters
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}     	% Type 1 fonts, similar to Computer Modern

\usepackage{microtype}				% Improves spacing

\usepackage{subfig}
\usepackage{subcaption}

\usepackage{tabularx}
\usepackage{booktabs}
%\newcolumntype{C}{>{\centering\arraybackslash}X} % centered version of "X" type
\setlength{\extrarowheight}{1pt}
\usepackage{enumerate}				% Additional options for listing of items in enumerate environment
\usepackage{todonotes}				% Adding todo items
\usepackage{dirtree}					% Simple display of directory tree
\usepackage{hyperref}					% Managing cross-referencing


\usepackage{lmodern}
\usepackage{nccmath}
\usepackage[keeplastbox]{flushend}
\usepackage{scalerel,stackengine}
\stackMath
\newcommand\reallywidehat[1]{%
	\savestack{\tmpbox}{\stretchto{%
			\scaleto{%
				\scalerel*[\widthof{\ensuremath{#1}}]{\kern.1pt\mathchar"0362\kern.1pt}%
				{\rule{0ex}{\textheight}}%WIDTH-LIMITED CIRCUMFLEX
			}{\textheight}% 
		}{2.4ex}}%
	\stackon[-6.9pt]{#1}{\tmpbox}%
}
\parskip 1ex

%Additional packages
\usepackage{mathptmx}
\usepackage{graphicx, subcaption}
\usepackage{array}
\usepackage{booktabs}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\usepackage{cleveref}
\renewcommand{\algorithmautorefname}{Algorithm}
\SetKwInput{KwPersistent}{Persistent variables}
\SetKwInput{KwLocal}{Local variable initializations}
\SetArgSty{textnormal}
\makeatletter
\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
\newcommand{\pushline}{\Indp}% Indent
\newcommand{\popline}{\Indm\dosemic}% Undent
%\let\oldnl\nl% Store \nl in \oldnl
%\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}% Remove line number for one line
%\newcounter{algoline}
%\newcommand\Numberline{\refstepcounter{algoline}\nlset{\thealgoline}}
%\AtBeginEnvironment{algorithm}{\setcounter{algoline}{0}}
\makeatother

\makeatletter
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\makeatother


%calligraphy packages
\usepackage{calrsfs}
\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
\newcommand{\Ca}{\pazocal{C}}
\newcommand{\Oa}{\pazocal{O}}
\newcommand{\Va}{\pazocal{V}}
\newcommand{\Ua}{\pazocal{U}}
\newcommand{\Aa}{\pazocal{A}}
\newcommand{\Ta}{\pazocal{T}}
\newcommand{\La}{\pazocal{L}}

\newcommand{\Ja}{\pazocal{J}}

\graphicspath{{./figures/}}
\usepackage{float}

\title{\LARGE \bf
Decentralized Strategy for Cooperative Multi-Robot Exploration and Mapping
}
\author{Ana Batinovi\'{c}, Juraj Or\v{s}uli\'{c}, Tamara Petrovi\'{c}, Stjepan Bogdan
	\thanks{Authors are with the University of Zagreb, Faculty of Electrical Engineering  and Computing, LARICS Laboratory for Robotics and Intelligent Control Systems, Unska 3, 10000 Zagreb, Croatia
        {\tt\small (ana.batinovic, juraj.orsulic, tamara.petrovic, stjepan.bogdan) at fer.hr}}}

\makeatletter
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\newcommand{\mb}[1]{\boldsymbol{#1}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

\makeatother

\begin{document}
\maketitle

\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

This work presents a novel approach to autonomous decentralized multi-robot frontier exploration and mapping of an unknown area.  The mobile robot team simultaneously explores the environment, discovers frontier points (points on the border between the explored and unexplored space), and communicates by fully connected graph and event-based communication in order to become dispersed throughout the environment. During the exploration, the amount of information exchanged between the robots is limited to data about the robot positions and their current target points. The main goal is to allocate the mobile robots to target frontier points in the environment in a way which minimises the overall exploration time. Moreover, mobile robots creates common map of the environment. The proposed strategy has been implemented in a simulation environment and compared with a coordinated exploration strategy. The simulation results demonstrate the effectiveness of the proposed decentralized multi-robot strategy.

\end{abstract}
\input{Content/introduction.tex}
\input{Content/exploration_and_mapping_overview.tex}
\input{Content/strategy_description.tex}
\input{Content/simulation_result.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CONCLUSION AND FUTURE WORK}
We have presented a modular approach to autonomous decentralized multi-robot exploration and  mapping which is, besides, not restricted to Google Cartographer SLAM and dense frontier detection. This strategy has demonstrated improved behaviour compared to the coordinated Burgard's strategy in term of exploration time. Another contribution of this work is a repository (available on Github\footnote{\href{https://github.com/larics/decentralized_multi_robot_exploration}{https://github.com/larics/decentralized\_multi\_robot\_exploration}}) that includes developed and implemented decentralized multi-robot exploration strategy as well as our implementation of the Burgard's algorithm. 

Despite these encouraging results, there are several aspects which could be improved. One of the interesting research direction is to consider decentralized map creating and complex data sharing. Also, an improvement can be a simpler simulator with more mobile robots, which we believe will approve better behaviour of our decentralized strategy over coordinated Burgard's strategy. Another direction can be an extension of the algorithm to cope with a limited communication range of the mobile robots, which will probably improve overall performance. Additionally, we want to investigate scenarios in which the robots may malfunction or break or in which the environment changes over time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{Bibliography/decentralized}

\end{document}
